% Nothing in Introduction
\addtocounter{section}{1}

\section{Production Sets}

\begin{prop}
    The production set $Y$ is additive and satisfies the nonincreasing returns condition if and only if it is a convex cone.
\end{prop}

\begin{prop}
    For any convex production set $Y \subset \mathbb{R}^L$ with $0 \in Y$, there is a constant returns, convex production set $Y' \subset \mathbb{R}^{L + 1}$ such that $Y = \{y \in \mathbb{R}^L: (y, -1) \in Y'\}$.
\end{prop}


\section{Profit Maximisation and Cost Minimisation}

\begin{prop}
    Suppose that $\pi(\cdot)$ is the profit function of the production set $Y$ and that $y(\cdot)$ is the associated supply correspondence. Assume also that $Y$ is closed and satisfies the free disposal property. Then
    \begin{enumerate}
        \item $\pi(\cdot)$ is homogeneous of degree one.
        \item $\pi(\cdot)$ is convex.
        \item If $Y$ is convex, then $Y = \{y \in \mathbb{R}^L: p \cdot y \leq \pi(p) \text{ for all } p \gg 0\}$.
        \item $y(\cdot)$ is homogeneous of degree zero.
        \item If $Y$ is convex, then $y(p)$ is a convex set for all $p$. Moreover, if $Y$ is strictly convex, then $y(p)$ is single-valued (if nonempty).
        \item (\emph{Hotelling's lemma}) If $y(\bar{p})$ consists of a single point, then $\pi(\cdot)$ is differentiable at $\bar{p}$ and $\nabla \pi(\bar{p}) = y(\bar{p})$.
        \item If $y(\cdot)$ is a function differentiable at $\bar{p}$, then $Dy(\bar{p}) = D^2 \pi(\bar{p})$ is a symmetric and positive semidefinite matrix with $Dy(\bar{p})\bar{p} = 0$.
    \end{enumerate}
\end{prop}

\begin{prop}
    Suppose that $c(p, w)$ is the cost function of a single-output technology $Y$ with production function $f(\cdot)$ and that $z(w, q)$ is the associated conditional factor demand correspondence. Assume also that $Y$ is closed and satisfies the free disposal property. Then
    \begin{enumerate}
        \item $c(\cdot)$ is homogeneous of degree one in $w$ and nondecreasing in $q$.
        \item $c(\cdot)$ is a concave function of $w$.
        \item If the sets $\{z \geq 0: f(z) \geq q\}$ are convex for every $q$, then $Y = \{(-z, q): w \cdot z \geq c(w, q) \text{ for all } w \gg 0\}$.
        \item $z(\cdot)$ is homogeneous of degree zero in $w$.
        \item If the set $\{z \geq 0: f(z) \geq q\}$ is convex, then $z(w, q)$ is a convex set. Moreover, if $\{z \geq 0: f(z) \geq q\}$ is a strictly convex set, then $z(p, w)$ is single-valued.
        \item (\emph{Shephard's lemma}) If $z(\bar{w}, q)$ consists of a single point, then $c(\cdot)$ is differentiable with respect to $w$ at $\bar{w}$ and $\nabla_w c(\bar{w}, q) = z(\bar{w}, q)$.
        \item If $z(\cdot)$ is differentiable at $\bar{w}$, then $D_w z(\bar{w}, q) = D^2_w c(\bar{w}, q)$ is a symmetric and negative semidefinite matrix with $D_w z(\bar{w}, q) \bar{w} = 0$.
        \item If $f(\cdot)$ is homogeneous of degree one (i.e. exhibits constant returns to scale), then $c(\cdot)$ and $z(\cdot)$ are homogeneous of degree one in $q$.
        \item If $f(\cdot)$ is concave, then $c(\cdot)$ is a convex function of $q$ (in particular, marginal costs are nondecreasing in $q$).
    \end{enumerate}
\end{prop}


% Nothing in The Geometry of Cost and Supply in the Single-Output Case
\addtocounter{section}{1}


\section{Aggregation}

\begin{prop}
    For all $p \gg 0$, we have
    \begin{enumerate}
        \item $\pi^* (p) = \sum_j \pi_j (p)$
        \item $y^* (p) = \sum_j y_j (p) \; (= \{\sum_j y_j : y_j \in y_j(p) \text{ for every } j\})$.
    \end{enumerate}
\end{prop}


\section{Efficient Production}

\begin{defn}
    A production vetor $y \in Y$ is \emph{efficient} if there is no $y' \in Y$ such that $y' \geq y$ and $y' \neq y$.
\end{defn}

\begin{prop}
    If $y \in Y$ is profit maximising for some $p \gg 0$, then $y$ is efficient.
\end{prop}

\begin{prop}
    Suppose that $Y$ is convex. Then every efficient production $y \in Y$ is a profit-maximising production for some nonzero price vector $p \geq 0$.
\end{prop}
